\begin{abstract}
Ethereum is the second most valueable cryptocurrency after bitcoin. The applications that can be built on Ethereum are countless. This was possible because of the introduction of the concept on smart contracts on ethereum. These smart contracts are immutable because thy are stored on blockchain. The immutable property is of great use for eradicating the trust issue when two parties agree to communicate using a smart contract. Smart contracts can work along with other smart contracts for example finishing of one smart contract can trigger execution of another smart contract etc. Despite of so many attractive promises made by smart contract, they can also be prone to problems. The immutability property which is of great use also pose issues in case a smart contract contains some bugs. The code of smart contract logic must be accurate and bug free. Otherwise it can be exploited for the wrong doings by the scammers. For example, the DAO hack\cite{dao} is an example of such wrong doings. The other major issue that arises because of such exploitation is that people will lose interest in the blockchain concept. Since this is a fairly new technology a good number of bugs are exposed by the community. Tools reporting various vulnerabilities are build in the recent times to aid coder to code bug free and accurate functionality smart contract.\\
The aim of this thesis is to build a tool that will flag DoS Vulnerable smart contract. The tool use symbolic execution to traverse all the possible paths in the smart contract. The tool test smart contracts for different number of invocations and variable path length that is traversed by symbolic execution. The symbolic executions and the path length are flexible parameters provided as input along with the smart contract to the tool. To test, the tool is run on a collected sample of 35 smart contracts with invocations 1 and 2 and path length 10, 20 and 40 respectively for both number of invocations.
\end{abstract}